\input{head.tex}

\begin{document}
\title{Key Financial Metrics for Early-Stage Genomics Companies}

\newcommand{\IPSNEO}{1}
\author[\IPSNEO]{Dylan Lawless %\thanks{Addresses for correspondence: \href{mailto:Dylan.Lawless@kispi.uzh.ch}{Dylan.Lawless@kispi.uzh.ch}}
}
\affil[\IPSNEO]{Switzerland Omics, Zürich, Switzerland.}

\maketitle
\justify

\section*{Acronyms}
\begin{acronym}
  \acro{ARR}[ARR]{Annual Recurring Revenue}
  \acro{CAC}[CAC]{Customer Acquisition Cost}
  \acro{LTV}[LTV]{Lifetime Value}
  \acro{SaaS}[SaaS]{Software as a Service}
\end{acronym}

\section*{Annual recurring revenue (\ac{ARR})}

\ac{ARR} is the total value of predictable, recurring revenue in a 12-month period. It is a key metric for evaluating the scalability and stability of businesses offering subscription or licensing-based services. Especially relevant for \ac{SaaS} or data-access models.

\textbf{Formula:}
\[
\text{\ac{ARR}} = \text{Monthly Recurring Revenue per Customer} \times \text{Number of Customers} \times 12
\]

\textbf{Example:}  
If 10 hospital labs are expected to pay CHF 12,000/year:
\[
\text{\ac{ARR}} = \text{CHF }12{,}000 \times 10 = \text{CHF }120{,}000
\]

\section*{Burn rate}

Burn rate refers to how much money a company spends each month, typically before generating revenue. It reflects your monthly net loss.

\textbf{Formula:}
\[
\text{Burn Rate} = \text{Monthly Expenses} - \text{Monthly Revenue}
\]

\textbf{Example:}  
If monthly expenses are CHF 10K and revenue is CHF 0:
\[
\text{Burn Rate} = \text{CHF }10{,}000
\]

\section*{Runway}

Runway is the amount of time (in months) a startup can continue operating at the current burn rate before exhausting its funds.

\textbf{Formula:}
\[
\text{Runway (months)} = \frac{\text{Cash on Hand}}{\text{Monthly Burn}}
\]

\textbf{Example:}  
With CHF 100K in cash and CHF 10K monthly burn:
\[
\text{Runway} = 10 \text{ months}
\]

\section*{Customer acquisition cost (\ac{CAC})}

\ac{CAC} measures the average cost to acquire one paying customer, factoring in marketing, sales, and onboarding costs.

\textbf{Formula:}
\[
\text{\ac{CAC}} = \frac{\text{Total Sales \& Marketing Costs}}{\text{Number of New Customers Acquired}}
\]

\section*{Lifetime value (\ac{LTV})}

\ac{LTV} estimates the total revenue a customer is expected to generate over their lifetime with your product or service.

\textbf{Formula:}
\[
\text{\ac{LTV}} = \text{Annual Revenue per Customer} \times \text{Average Retention (in years)}
\]

\section*{Gross margin}

Gross margin reflects how much profit remains after accounting for the cost of delivering the service. For data and software businesses, margins are typically high.

\textbf{Formula:}
\[
\text{Gross Margin} = \frac{\text{Revenue} - \text{Cost of Goods Sold}}{\text{Revenue}}
\]

\section*{Focus areas while pre-revenue}

\begin{itemize}[leftmargin=*]
  \item Know your burn rate and runway precisely.
  \item Define a clear pricing model (per report, per hospital, annual licence).
  \item Model a realistic \ac{ARR} path based on pilots and current usage.
  \item Prepare a 12–24 month financial plan outlining projected costs (hires, cloud infrastructure, compliance, legal, sales).
\end{itemize}


\bibliographystyle{unsrtnat}
\bibliography{references}

\end{document}





